### 2018-06-29 Thesis/Parts/Data/Data.tex
Update

Figure~\ref{figure:tfidfPerformance} shows the performance of title and abstract as median rank, and figure~\ref{figure:tfidfMemory} shows the storage size in gigabyte, of the 1k/1K, 4K/4K, 7K/7K and 10K/10K TF-IDF configurations. This plot shows that, while the required storage size keeps rising, the performance on title quickly stagnates, and the performance on abstract follows too. Given this information, we have chosen to use the 10K/10K, 10K/5K and 5K/5K configurations to compare our embedding results to. The TF-IDF features are created on article level. We average the set of article feature vectors to create a journal feature vector, just as we did with the embeddings. 

>>>>

Figure~\ref{figure:tfidfPerformance} shows the performance of title and abstract as median rank, and figure~\ref{figure:tfidfMemory} shows the storage size in gigabyte, of the 1k/1K, 4K/4K, 7K/7K and 10K/10K TF-IDF configurations. This plot shows that, while the required storage size stagnate, the performance on title also quickly stagnates, together with the performance on the abstracts. Given this information, we have chosen to use the 10K/10K, 10K/5K and 5K/5K configurations to compare our embedding results to. Since these configurations can be kept in memory (storage size) while it is not likely that larger sets will give much improvement. The TF-IDF features are created on article level. We average the set of article feature vectors to create a journal feature vector, just as we did with the embeddings. 
